A secondary screen architecture to accurately capture viewer interactions in interactive TV environments

### 2014-05-02 src/paper.tex
Abstract rewriting

\begin{abstract}
Watching TV is frequently seen as a social activity. Groups of people gather around the television for entertainment or information. One important application for TV viewers is content personalization, which consists in generating personalized content based on viewer interactions. Since the TV set is shared by many people, it is difficult to accurately capture the individual interactions from every viewer using a traditional remote control. As a new trend, the proliferation of personal mobile devices has changed the habits on audiovisual content consumption in interactive TV environments. In many situations people use their personal devices as a secondary screen to perform activities related to television watching. In this paper, we present an architecture for secondary screen devices that facilitates the capture of individual viewer interactions to use in content recommendation. In addition, this architecture can enhance the viewer interaction without interrupting the collective experience while watching TV.
\end{abstract}

@@

Watching TV is essentially a social activity, where family, friends, or people with a common interest share the same space and TV set for entertainment or information~\cite{Masthoff2004}. After many advances in technologies for interactive and digital TV it is possible to develop high level applications to enrich the TV experience. One important application is content personalization, in which content providers deliver personalized content to viewers based on their preferences.

@@

>>>>

\begin{abstract}
TV watching is frequently seen as a social activity. People gather around the television for entertainment or information. Advances in TV technology have enabled the viewer to actively interact with applications and providers instead of just passively watch TV. One important application for the viewers is content personalization, which consists in generating content recommendations based on viewers' interactions. Since the TV set is shared by many people, it is difficult to accurately capture the individual interactions from every viewer using a traditional remote control. In this paper, we present an architecture that facilitates the identification of viewers and the capture of their individual interactions in shared TV environments. In addition, we present an area of application of this architecture in the recommender systems domain.
\end{abstract}

@@

TV watching is essentially a social activity, where family, friends, or people with a common interest share the same space and TV set for entertainment or information~\cite{Masthoff2004}. After many advances in technologies for interactive and digital TV it is possible to develop high level applications to enrich the TV experience. One important application is content personalization, in which content providers deliver personalized content to viewers based on their preferences.

@@

people rarely just sit passively and watch TV

As a new trend, the proliferation of personal mobile devices has changed the habits on audiovisual content consumption in interactive TV environments. In many situations people use their personal devices as a secondary screen to perform activities related to television watching.

In addition, this architecture can enhance the viewer interaction without interrupting the collective experience while watching TV.
